### 2024-02-05 README.Rmd
improve readme

# sfislands <img src="man/figures/logo.png" align="right" height="120" alt="" />

@@

The goal of `sfislands` is to make it easier to deal with geographic datasets which contain islands.

@@

`sfislands` is intended to be used alongside the `sfdep` package. The principal functions from `sfdep` for areal data are demonstrated in its vignette using the `guerry` dataset. This data applies to the geographical area of mainland France as shown below:

@@

Returning to the dataset used in `sfdep`, we can easily create a smooth of suicides in France in 1831 as follows. Since there are no islands, we use `st_bridges()` and it will function like `sfdep:st_contiguity()` except that it automatically adds a contiguity 'nb' column to the dataframe.

>>>>

# sfislands <img src="man/figures/logo.png" align="right" height="120"/>

@@

The goal of `sfislands` is to make it easier to deal with geographic datasets which contain islands. It does so using a tidy framework in the spirit of Josiah Parry's [sfdep](https://sfdep.josiahparry.com/) package.

@@

`sfislands` is intended to be used alongside the `sfdep` package. The principal functions from `sfdep` for areal data are demonstrated in its vignette using the `guerry` ("*Essay on the Moral Statistics of France*") dataset. This data applies to the geographical area of mainland France as shown below:

@@

Returning to the dataset used in `sfdep`, we can easily create a smooth of suicides in France in 1830 as follows. Since there are no islands, we use `st_bridges()` and it will function like `sfdep:st_contiguity()` except that it automatically adds a contiguity 'nb' column to the dataframe.
